\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-01-11 manuscript.Rnw
Typo fix

The parameters of a survival model are stored in a \code{params_surv} object and a \code{params_surv_list} can be used to store the parameters of multiple survival models. The latter is useful for storing the parameters of a multi-state model or the independent survival models required for a PSM. The parameters of a multinomial logistic regression are stored in a \code{params_mlogit} and can be created by fitting a model for each row in a transition probability matrix with \code{nnet::multinom()}.

>>>>

The parameters of a survival model are stored in a \code{params_surv} object and a \code{params_surv_list} can be used to store the parameters of multiple survival models. The latter is useful for storing the parameters of a multi-state model or the independent survival models required for a PSM. The parameters of a multinomial logistic regression are stored in a \code{params_mlogit} object and can be created by fitting a model for each row in a transition probability matrix with \code{nnet::multinom()}.
